Simulation Tools for Small Area Estimation: Introducing the \proglang{R}-package \proglang{saeSim}

### 2015-01-23 replies_to_referee/Replies_to_referee.tex

\documentclass[11pt]{article}

\usepackage{setspace}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amsmath, amsthm, amssymb}
%\usepackage{revsymb}
%\usepackage{eurosym}
\usepackage[pdftex]{graphicx}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{lscape}
\usepackage{color}
\usepackage[figuresright]{rotating}
\newtheorem{thm}{Theorem}[section]
\newcommand{\sgn}{\text{sgn}}

\setlength{\textwidth}{15cm}
\setlength{\textheight}{23cm} \topmargin-1cm %\evensidemargin2cm
\oddsidemargin1cm

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bed}{\begin{displaymath}}
\newcommand{\eed}{\end{displaymath}}
%
% MATH -------------------------------------------------------------------
\newcommand{\U}{{\cal U}}
\newcommand{\R}{{\cal R}}
\newcommand{\abs}[1]{\left\vert#1\right\vert}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\bra}[1]{\left(#1\right)}
\newcommand{\braq}[1]{\left[#1\right]}

\newcommand{\eps}{\varepsilon}
\newcommand{\si}{\sigma}
\newcommand{\ka}{\kappa}
\newcommand{\tr}{^{T}}
\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\bGamma}{\boldsymbol{\Gamma}}
\newcommand{\ppsi}{\vec{\psi}}
\newcommand{\bpsi}{\vec\psi}
\newcommand{\btheta}{\vec\theta}
\newcommand{\bomega}{\vec\omega}
\newcommand \bDelta {\vec\Delta}
\newcommand{\bgamma}{\vec{\gamma}}
\newcommand{\beps}{\vec{\varepsilon}}

\def \cI {{\cal I}}
\def \bA {{\mathbf A}}
\def \bB {{\mathbf B}}
\def \bC {{\mathbf C}}
\def \bD {{\mathbf D}}
\def \bb {{\mathbf b}}
\def \be {{\mathbf e}}
\def \bG {{\mathbf G}}
\def \bH {{\mathbf H}}
\def \bh {{\mathbf h}}
\def \bI {{\mathbf I}}
\def \bL {{\mathbf L}}
\def \bn {{\mathbf n}}
\def \br {{\mathbf r}}
\def \bP {{\mathbf P}}
\def \bq {{\mathbf q}}
\def \bQ {{\mathbf Q}}
\def \bR {{\mathbf R}}
\def \bs {{\mathbf s}}
\def \bt {{\mathbf t}}
\def \bX {{\mathbf X}}
\def \bx {{\mathbf x}}
\def \by {{\mathbf y}}
\def \bu {{\mathbf u}}
\def \bv {{\mathbf v}}
\def \bV {{\mathbf V}}
\def \bZ {{\mathbf Z}}
\def \bz {{\mathbf z}}
\def \bW {{\mathbf W}}
\def \bw {{\mathbf w}}
\def \zero {{\mathbf 0}}

\def \diag {\mbox{diag}}
\def \uno {\mathbf 1}

\def \diag {\mbox{diag}}
\def \uno {\mathbf 1}
%\def\b#1{\mbox{\boldmath $#1$}}    % - \b: bold in formulas
%\def\bl#1{\mbox{\footnotesize \boldmath {$#1$}}} % - \bl: bold little formulas
\def\m#1{\mbox{#1}}                % - \m: text in formulas
\def\ml#1{\mbox{\scriptsize #1}} % - \ml: little text in formulas
\def\ha#1{\mbox{$\hat{\b #1}$}}
%\def\vec#1{\mbox{\boldmath $#1$}}

\newcommand{\sumuni}{\sum_{i\in\U}}
\newcommand{\sums}{\sum_{i\in s}}

\newcommand{\tcr}{\textcolor{red}}
\newcommand{\tcb}{\textcolor{blue}}

\newtheorem{Theorem}{Theorem}
\newtheorem{Remark}{Remark}
\newtheorem{Lemma}{Lemma}
\newtheorem{Corollary}{Corollary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The \cite command functions as follows:
 %   \citet{key} ==>>                Jones et al. (1990)
 %   \citet*{key} ==>>               Jones, Baker, and Smith (1990)
 %   \citep{key} ==>>                (Jones et al., 1990)
 %   \citep*{key} ==>>               (Jones, Baker, and Smith, 1990)
 %   \citep[chap. 2]{key} ==>>       (Jones et al., 1990, chap. 2)
 %   \citep[e.g.][]{key} ==>>        (e.g. Jones et al., 1990)
 %   \citep[e.g.][p. 32]{key} ==>>   (e.g. Jones et al., p. 32)
 %   \citeauthor{key} ==>>           Jones et al.
 %   \citeauthor*{key} ==>>          Jones, Baker, and Smith
 %   \citeyear{key} ==>>             1990

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{{Simulation Tools for Small Area Estimation:\\
Introducing the R-package saeSim} \\Replies to referee}
\author{S. Warnholz
\and T. Schmid
}

\date{} \maketitle

%\begin{abstract}
%This is the abstract
%\end{abstract}

%\textbf{Keywords:} These are the keywords.

%\doublespacing

\textcolor{red}{We are very grateful to the Editor and the two reviewers for their constructive comments. We have done our best to incorporate them in the revision. The following notes explain how we addressed each comment.}

\section*{Replies to reviewer A}

The manuscript introduces the R package saeSim, which simplifies writing code for simulation studies in small area statistics. The manuscript is enjoyable to read, but contains some shortcomings as well as several typos and other mistakes. The software seems useful for small area statisticians and could be a valuable contribution to the community. I particularly like the notion of treating simulation as a data manipulation process.

\vspace{0.5cm}

\noindent There are only minor issues that need to be addressed.

\begin{itemize}
\item
	Page 2: The authors cite Kolb (2013) for synthetic data generation. They should also mention what is available in R, for instance the approach by Alfons, Kraft, Templ \& Filzmoser (2011, Statistical Methods \& Applications) that is implemented in package simPop.

	\textcolor{red}{We mow reference Alfons, Kraft, Templ \& Filzmoser (2011, Statistical Methods \& Applications) together with Kolb (2013). The R-package simPop is now mentioned in the paragraph where we also cite simFrame, also on page 2.}

\item
	Page 2: The authors mention NUTS levels without explaining what they are. Please add a short explanation, including what the abbreviation NUTS stands for.

	\textcolor{red}{We deleted the reference to the NUTS levels. After revision the paragraph looses no relevant information to follow the argument. The revised version is now as follows:}

	\begin{quote}
	\textit{\textcolor{red}{
	Survey statistics are used, for example, in order to deliver specific indicators as a basis for
economic and political decision processes. Especially regional or group-specific comparisons
are of interest (cf. Schmid and Münnich 2014). Surveys which shall provide sufficient data
for these regional indicators, however, are generally designed for larger areas. Hence, sample
information on more detailed levels, e.g. municipalities, is hardly available so that classical
estimation methods (direct estimators) may lead to high variances of the estimates (cf. Ghosh
and Rao 1994). In this case, small area estimation methods may reveal highly improved results
for the target estimates. Small area estimation has become more and more attractive over
the last decade:
	}}
	\end{quote}

\item
	Page 5, last paragraph: I'm not sure which line in the simple example for the pipe operator is more readable. The line "sum(1:10)" translates into "sum of 1 to 10". The line "1:10 \%$>$\% sum" tanslates into "generate 1 to 10, then take the sum". I'm sure that the authors can find a simple example that is better suited to illustrate their point.

	\textcolor{red}{We changed the example into:}
	\verb'colMeans(matrix(rnorm(10), ncol = 2))' \textcolor{red}{which translates to} \verb'rnorm(10) %>% matrix(ncol = 2) %>% colMeans' \textcolor{red}{, and is now an actual improvement in readability.}

\item
	Page 6 and 7, code examples: The authors load package saeSim in each of the two code examples. Yet there is another code chunk before those examples which use functionality from the package. If readers try to execute all code in the order it appears in the paper, they will get error messages. I suggest to load the package in the beginning of Section 4 (in a separate chunk), and to remove this line from the two examples to focus on the relevant code.

	\textcolor{red}{We now load saeSim (and magrittr) in the beginning of section 4. We checked the code again, so that all expressions are valid when executed in the order in which they appear in the article. Also we made the seed available to the reader. Furthermore the package sae produced naming conflicts as it loads a lot of dependencies. We do not load the package but reference to it with the '::' operator, which is acceptable as we only use two functions from this package.}

\item
	Page 8, last line: The authors write "... we store these data tables...". Are those data frames or data tables? In R, this can be confusing due to the data.table package.

	\textcolor{red}{To avoid any confusion we changed it into 'data frame'. The paragraph is quoted as a reply to you next remark.}

\item
	Page 9: The authors state that they store some information as attritutes to the main data frame. Attributes can be a dangerous thing in R as there are some functions for manipulating data that may remove any attributes. Please give a discussion on this issue and provide more motivation for using attributes.

	\textcolor{red}{We agree that relying on attributes can be a weakness. The problem is, that very often we do not have a single data frame to process, but also meta data attached. We can make that meta data available by taking advantage of R's lexical scoping rules. However, this is a dangerous path as the functions in which we need that meta data are no longer self contained. They depend on the state of objects other than their arguments and we want to avoid that. Another possibility is to make meta data available only to the functions in which they are needed by using closures. This ensures that the functions are self contained but adds unnecessary complexity for the purpose of this article as advanced functional programming techniques are not "mainstream" for R users. Also we could design an own \textit{data class} which is more formal to ensure type consistency (for example using a S4-class). However, we tried to design saeSim such that it can be used with as many existing tools as possible. We think this is possible by sticking to the "data.frame in, data.frame out" philosophy. Thus, we decided to support functions which preserve attributes. All present functions in the package will preserve attributes of the main data frame. If you have suggestions to improve this we would appreciate it. We added the discussion in a separate paragraph as follows:}
	\begin{quote}
	\textit{
	\textcolor{red}{Before we begin to construct the simulation setup, we store these data frames as attributes
to the population data. However, extra care is is needed because not all functions for
manipulating data frames in R will preserve their attributes. Functions in saeSim all support
this approach. Yet, in user defined functions this needs to be kept in mind by the author.
Adding attributes to the data is a very flexible form of processing data on different aggregation
levels and we believe this to be a reasonable trade-off. Of course other options can be applied
within the possibilities of the R language.
	}
	}
	\end{quote}
\item
	Page 13: To the best of my knowledge, the preferred format for CRAN links is http://CRAN.R-project.org/package=saeSim (also note the capitalization of CRAN and R).\textcolor{red}{ -- done}
\item
	Page 13: For non-representative outliers, the authors give the explanation "outliers are part of the sample but not the population". This may be confusing to some readers. I suggest that they add "e.g., incorrectly recorded values".\textcolor{red}{ -- done}

\end{itemize}

\vspace{0.5cm}

\noindent Comments regarding language are given in the following. There may be more mistakes, hence I recommend that the authors ask a colleague to proofread the manuscript (preferably an English native speaker).

\noindent\textcolor{red}{Our apologies for the inconvenience for proofreading the article. We followed your suggestion and the manuscript has been proofread again.}

\begin{itemize}
\item
	Page 1, abstract and first paragraph: "has been substantially grown" to "has grown" \textcolor{red}{-- done}
\item
	Page 3, line -8: "is build on a sampling model" to "is built on a sampling model" \textcolor{red}{-- done}
\item
	Page 4, line -2: "different point of views" to "different points of view" \textcolor{red}{-- done}
\item
	Page 6, lines 1-2: "In saeSim, we rely on this operator, although all functions can be used without, we strongly recommend to use it." to "In saeSim, we rely on this operator. Although all functions can be used without it, we strongly recommend its usage." \textcolor{red}{-- done}
\item
	Page 6, second paragraph: "... which has a data.frame as input as well as return value." The correct "... which has a data.frame as input as well as as return value." is cumbersome since as appears twice in a row, so I suggest to change this to "... which has a data.frame both as input and as return value."  \textcolor{red}{-- done}

\item
	Page 10, first paragraph: "This focus on the definition of each component and on meeting the convention of the defined interface is the intended approach." I'm confused by this sentence, please rephrase.

	\textcolor{red}{We deleted the sentence as their seems to be no loss of information. The paragraph now reads as:}	
	\begin{quote}
	\textit{
	\textcolor{red}{
		In the next step, we define components which add the estimates of interest to the data. Here we compute the direct estimator of the mean income in each domain and the EBLUP under the BHF model. Although this could be done in one step, we separate the two computations to illustrate how to combine several estimations and how to define each component independent of each other. This automatically organises the simulation and each component is arranged using the simulation framework. Hence, we define two functions, one for adding the direct estimates and one for adding the EBLUP.
		}
		}
	\end{quote}
\item
	Page 13, second paragraph: "version-control" to "version control" \textcolor{red}{-- done}
\item
	Page 13, second paragraph: "it's purpose" to "its purpose" \textcolor{red}{-- done}
\end{itemize}

\pagebreak
\section*{Replies to reviewer C}

The package appears to be useful for most statisticians working with small area methods. It is a good idea to build the framework using the idea of process of data manipulation. This makes the package easy to use. The manuscript is interesting and useful, and I find it acceptable for
publishing after minor revision.

\begin{itemize}
\item
	The authors should mention - probably in Section 4 - that in order to repeat a simulation with identical results, the seed used in the original simulation has to be known.

	\textcolor{red}{We added this information right before we start illustrating the model-based simulation. Also we added the seed visibly in the code as before it was set in a hidden chunk. The second paragraph in section 4.1 now reads as follows:}
	\begin{quote}
	\textit{
\textcolor{red}{In this case the \textit{base-component} is a data frame with an id variable named idD and constructed with the function base\_id. Any random number generator in R can be used. However, we have normally distributed variates, for which some predefined functions are available in the package. For the reproducibility of the following results we also set the seed to 1. The seed is not part of a simulation setup in saeSim but needs to be supplied by the researcher.
	}
	}
	\end{quote}
\end{itemize}

\vspace{0.5cm}

\noindent There are some grammatical errors:

\begin{itemize}
\item
	(1) abstract: remove 'been' from "...has been substantially grown" \textcolor{red}{-- changed to: "... has grown substantially"}
\item
	(2) Introduction: remove 'been' from "...has been substantially..." \textcolor{red}{-- changed to: "... has grown substantially"}
\item
	(3) Introduction (last two lines on page 1): rephrase "...reproducible research aims that the full output of the academic research,..." using "...aims at the availability of the full... " \textcolor{red}{-- done}
\item
	(4) Replace 'neighboured' by 'neighbouring' \textcolor{red}{-- done}
\item
	(5) At the end of page 1, remove '-' in "source-code" \textcolor{red}{-- done}
\item
	(6) In the beginning of section 2 (second line), replace 'less' by 'few' in "...for domains where less or no sampled..." \textcolor{red}{-- done}
\item
	(7) Below equation (1), replace 'build' by 'built' in "...introduced by Fay and Herriot (1979) is build..." \textcolor{red}{-- done}
\end{itemize}

\end{document}

### 2015-01-23 saeSim.Rnw
replies and changes referee 1

@@

%% additional packages
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{subcaption}

@@

%% an abstract and keywords
\Abstract{
The demand for reliable regional estimates from sample surveys has been substantially grown over the last decades. Small area estimation provides statistical methods to produce reliable predictions when the sample sizes in regions are too small to apply direct estimators. Model- and design-based simulations are used to gain insights into the quality of the introduced methods. In this article we present a framework which may help to guarantee the reproducibility of simulation studies in articles and during research. The introduced \proglang{R}-package \proglang{saeSim} is adjusted to provide a simulation environment for the special case of small area estimation. The package may allow the prospective researcher during the research process to produce simulation studies with a minimal effort of coding.   
}

@@

%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%
%% include your article here, just as usual
%
% R CMD Sweave %.Rnw
% Loading (and installing) necessary packages.
<<echo=FALSE>>=
loadAndInstallPackage <- function(packageName) {
  if(!eval(substitute(suppressPackageStartupMessages(require(packageName))))) {
    install.packages(packageName)
    eval(substitute(suppressPackageStartupMessages(library(packageName))))
  } 
}
loadAndInstallPackage("saeSim")
# Keep order in which packages are loaded, there are naming conflicts between dependencies (MASS and dplyr):
loadAndInstallPackage("sae")
loadAndInstallPackage("dplyr")
loadAndInstallPackage("reshape2")
loadAndInstallPackage("ggplot2")
@
%
\section{Introduction}
The demand for reliable small area statistics from sample surveys has been substantially grown over the last decades due to their use in public and private sectors. In this paper we present a framework for simulation studies inside the field of small area estimation. This tool might be useful for the prospective researcher or data analyst to provide reproducible research.

Reproducible research has become a widely discussed topic. In the field of statistics many open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, dynamic reporting packages like \proglang{knitr} \citep{yihui13}, \proglang{sweave} \citep{leisch02} and more recently \proglang{rmarkdown} \citep{allaire14}, make the integration of text and source code for statistical analysis possible. Publishing source code and data alongside research results draws special attention to authoring the analysis. However, the requirements for source code are different from the written words in the article itself.

@@

Next to the combination of text and source code, reproducible research aims that the full output of the academic research, which is the paper combined with the full computational environment like data and source code, is available. However, real data is often very sensitive and governed by strict confidentiality rules. Synthetic data generation mechanisms \citep{Kol11} can be used to provide safe data which is publicly available to enable the community to reproduce the analysis and results. \cite{Bur14} interpreted this as an open research philosophy. Such synthetic data sets can be used to test newly proposed statistical methods in a close-to-reality framework. 
%This may provide valuable insights about the quality of the introduced methods in a controlled environment under different scenarios. 
In general, simulation studies in statistics can be divided into two concepts:
%
\begin{itemize}
\item Design-based: The simulation study is based on true or synthetic data of a fixed population. Then, samples are selected repeatedly from the underlying finite population and different estimation methods are applied in each replication. The obtained estimates are compared to the true values of the population, for instance, in terms of relative bias (RB) or relative root mean squared error (RRMSE).
\item Model-based: The simulation study uses data drawn from certain distributions. In each iteration, the population is generated from a model and a sample is selected according to a specific sampling scheme. The sample is used to estimate the quantity of interest and quality measures (like RB and RRMSE) are derived.  
\end{itemize}
Further discussion regarding model- and design-based simulations is available in \cite{Mue03}, \cite{Sal10} or \cite{Alf10}.

\cite{Alf10} provide the \proglang{R}-package \proglang{simFrame} which helps to conduct simulation studies in a reproducible environment. It includes a wide range of different features (like data generation, sampling schemes, outlier contamination mechanisms and missing values) to conduct simulation studies. \proglang{simFrame} was originally developed for simulations in the context of survey statistics but is now designed to be as general as possible \citep[cf.][]{Alf10}.

Survey statistics are used, for example, in order to deliver specific indicators as a basis for economic and political decision processes. Especially regional or group-specific comparisons are of interest \citep[cf.][]{Sch13}. Surveys which shall provide the sufficient data for these regional indicators, however, are generally designed for larger areas (NUTS 1-2 level). Hence, sample information on more detailed levels, like NUTS3, is hardly available so that classical estimation methods (direct estimators) may lead to high variances of the estimates \citep[cf.][]{Gho94}. In this case, small area estimation methods may reveal highly improved results for the target estimates. Small area estimation has become more and more attractive over the last decade:

@@

However, simulation studies in the context of small area estimation is often presented very briefly. Thus, there is a need to have a suited framework to guarantee the reproducibility of analysis. To the best of our knowledge, there is not any \proglang{R}-package or framework adjusted for the special case of small area estimation which provides a simulation environment.

The aim of this article is to introduce a new \proglang{R}-package, \proglang{saeSim}, which supports the process of making simulation studies in the field of small area estimation reproducible. To be more precise, the package has three main objectives: First, provide tools for data generation. Second, unify the process of simulation studies. Third, make the source-code of simulation studies available, such that it supports the conducted research in a transparent manner.

@@

The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where less or no sampled units are available. Groups may be areas or other entities, for example defined by socio-economic characteristics. The demand for such estimators is rising as they are used for fund allocation, educational and health programs \citep{pfeffermann13}. As direct estimation of such statistics are considered to be unreliable (with respect to MSE), methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains. This can be achieved by using additional information from census data or registers to assist the prediction for non-sampled domains or domains with small sample sizes.

@@

Due to reasons of confidentiality unit-level information is not always available. Instead only aggregates for the domains or direct estimators may be supplied. In this case the feasible direct estimates are known to be unreliable in the case of small sample sizes. Here area-level models can be valuable. The area-level model introduced by \cite{fay79} is build on a sampling model:
%
\[\directStat_{\indexDomain} = \trueStat_{\indexDomain} + \samplingError_{\indexDomain},\]
%
where $\directStat_{\indexDomain}$ is a direct estimator of a statistic of interest $\trueStat_{\indexDomain}$ for an area $\indexDomain$. The sampling error $\samplingError_{\indexDomain}$ is assumed to be independent and normally distributed with known variances $\samplingVarianceIndexed$, i.e. $\samplingError_{\indexDomain}|\trueStat_{\indexDomain} \sim \mathit{N}(0, \samplingVarianceIndexed)$. The model assumes a linear relationship between the true area statistic $\trueStat_{\indexDomain}$ and some auxiliary variables $\xArea$:
%
\[\trueStat_{\indexDomain} = \xArea^\top \beta + \randomEffectIndexed,\] 
%
with $\indexDomain=1,\dots, \nDomains$. 
%Note that $\xArea$ is a vector containing area-level (aggregated) information for $\nRegressor$ variables and $\beta$ is a vector ($1\times \nRegressor$) of regression coefficients describing the (linear) relationship. 
The model errors $\randomEffectIndexed$ are assumed to be independent and normally distributed, i.e. $\randomEffectIndexed \sim \mathit{N}(0, \randomEffectVariance)$. Furthermore $\samplingErrorIndexed$ and $\randomEffectIndexed$ are assumed to be independent. Combining the sampling and linking model leads to:
\begin{equation}
\label{eq:FH}
\directStatIndexed = \xArea^\top \beta + \randomEffectIndexed + \samplingErrorIndexed.
\end{equation} 
%
The Fay-Herriot (FH) model in (\ref{eq:FH}) is effectively a random-intercept model where the distribution of the error term $\samplingErrorIndexed$ is heterogeneous and known. The EBLUP of the small area mean in the FH model is given by 
\begin{eqnarray}\label{FHEBLUP}\hat{\overline{y}}_i^{FH}&=&\xArea^\top \hat{\beta} + \hat{\randomEffectIndexed}.
\end{eqnarray}

@@

Simulation studies in small area estimation address three different levels, the population, the sample and data on aggregated level. Figure \ref{fig:flowdiagram} illustrates these levels. The left column describes the steps of data manipulation, the right column presents the function names to define the corresponding steps. The \textbf{population-level} defines the data on which a study is conducted and may be a true population, synthetic population data or randomly generated variates from a model. We see two different point of views to define a population: Firstly, \textit{design-based} simulations, which means that a simulation study is based on true or synthetic data of \textit{one} population. Secondly, \textit{model-based} simulations, which have changing random populations drawn from a model.

@@

\section{Case studies}
\label{sec:caseStudy}
We present two applications of \proglang{saeSim}, one model-based simulation in Section \ref{sec:csModel} and a design-based simulation in Section \ref{sec:csDesign}. Before, we introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation. The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}. As a simple example see the following lines which are equivalent:

<<eval=FALSE>>=
sum(1:10)
1:10 %>% sum
@

In \proglang{saeSim} we rely on this operator, although all functions can be used without, we strongly recommend to use it. The following example shows some of the aspects of the package:

<<eval=FALSE>>=
setup1 <- sim_base_lm() %>% sim_sample(sample_number(5))
setup2 <- sim_base_lm() %>% sim_sample(sample_fraction(0.05))
@

Without knowing anything about the setup defined in \proglang{sim\_base\_lm} we notice that \proglang{setup1} and \proglang{setup2} only differ in the applied sampling scheme. \proglang{sim\_sample} is responsible to control when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples. Separating the responsibility of each component into what is applied and when it is applied makes it possible to add new components to any step in the process. The composition of a simulation in that manner will focus on the definition of components and hide control structures. Any function can be passed to \proglang{sim\_sample} which has a \proglang{data.frame} as input as well as return value. The only responsibility of that function is to draw a sample, which makes it easy to find, understand and reuse when published. The operator \proglang{\%>\%} is used to add new components to the setup.

>>>>

%% additional packages and settings which are not part of the template:
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{subcaption}

@@

@@

%% an abstract and keywords
\Abstract{
The demand for reliable regional estimates from sample surveys \red{has grown substantially} over the last decades. Small area estimation provides statistical methods to produce reliable predictions when the sample sizes in regions are too small to apply direct estimators. Model- and design-based simulations are used to gain insights into the quality of the introduced methods. In this article we present a framework which may help to guarantee the reproducibility of simulation studies in articles and during research. The introduced \proglang{R}-package \proglang{saeSim} is adjusted to provide a simulation environment for the special case of small area estimation. The package may allow the prospective researcher during the research process to produce simulation studies with a minimal effort of coding.   
}

@@

%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\red}[1]{\color{red} #1 \color{black} }

\begin{document}
%
%% include your article here, just as usual
%
% R CMD Sweave %.Rnw
% Loading (and installing) necessary packages.
<<echo=FALSE>>=
# loadAndInstallPackage <- function(packageName) {
#   if(!eval(substitute(suppressPackageStartupMessages(require(packageName))))) {
#     install.packages(packageName)
#     eval(substitute(suppressPackageStartupMessages(library(packageName))))
#   } 
# }
# loadAndInstallPackage("saeSim")
# # Keep order in which packages are loaded, there are naming conflicts between dependencies (MASS and dplyr) which are loaded and attached by the package sae:
# loadAndInstallPackage("sae")
# loadAndInstallPackage("dplyr")
# loadAndInstallPackage("reshape2")
# loadAndInstallPackage("ggplot2")
@
%
\section{Introduction}
The demand for reliable small area statistics from sample surveys \red{has grown substantially} over the last decades due to their use in public and private sectors. In this paper we present a framework for simulation studies inside the field of small area estimation. This tool might be useful for the prospective researcher or data analyst to provide reproducible research.

Reproducible research has become a widely discussed topic. In the field of statistics many open source tools like the \proglang{R}-language \citep{r14} and \LaTeX, dynamic reporting packages like \proglang{knitr} \citep{yihui13}, \proglang{sweave} \citep{leisch02} and more recently \proglang{rmarkdown} \citep{allaire14}, make the integration of text and source code for statistical analysis possible. Publishing source code and data alongside research results draws special attention to authoring the analysis. However, the requirements for source code are different from the written words in the article itself.

@@

Next to the combination of text and source code, reproducible research aims at the availability of the full academic research, which is the paper combined with the full computational environment like data and source code. However, real data is often very sensitive and governed by strict confidentiality rules. \red{Synthetic data generation mechanisms as discussed in \cite{alfons2011} and \cite{Kol11} can be used to provide safe data which is publicly available to enable the community to reproduce the analysis and results.} \cite{Bur14} interpreted this as an open research philosophy. Such synthetic data sets can be used to test newly proposed statistical methods in a close-to-reality framework. 
%This may provide valuable insights about the quality of the introduced methods in a controlled environment under different scenarios. 
In general, simulation studies in statistics can be divided into two concepts:
%
\begin{itemize}
\item Design-based: The simulation study is based on true or synthetic data of a fixed population. Then, samples are selected repeatedly from the underlying finite population and different estimation methods are applied in each replication. The obtained estimates are compared to the true values of the population, for instance, in terms of relative bias (RB) or relative root mean squared error (RRMSE).
\item Model-based: The simulation study uses data drawn from certain distributions. In each iteration, the population is generated from a model and a sample is selected according to a specific sampling scheme. The sample is used to estimate the quantity of interest and quality measures (like RB and RRMSE) are derived.  
\end{itemize}
Further discussion regarding model- and design-based simulations is available in \cite{Mue03}, \cite{Sal10} or \cite{Alf10}.

\red{\cite{Alf10} provide the \proglang{R}-package \proglang{simFrame} which helps to conduct simulation studies in a reproducible environment. It includes a wide range of features (like data generation, sampling schemes, outlier contamination mechanisms and missing values) to conduct simulation studies. \proglang{simFrame} was originally developed for simulations in the context of survey statistics but is now designed to be as general as possible \citep[cf.][]{Alf10}. Furthermore the package \proglang{simPop} \citep{Alf14} supports the generation of synthetic population data. This can be a suitable environment in scenarios where the reproducibility of results and confidentiality issues both play an important role.}

Survey statistics are used, for example, in order to deliver specific indicators as a basis for economic and political decision processes. Especially regional or group-specific comparisons are of interest \citep[cf.][]{Sch13}. Surveys which shall provide sufficient data for these regional indicators, however, are generally designed for larger areas. Hence, sample information on more detailed levels, e.g. municipalities, is hardly available so that classical estimation methods (direct estimators) may lead to high variances of the estimates \citep[cf.][]{Gho94}. In this case, small area estimation methods may reveal highly improved results for the target estimates. Small area estimation has become more and more attractive over the last decade:

@@

However, simulation studies in the context of small area estimation \red{are} often presented very briefly. Thus, there is a need to have a suited framework to guarantee the reproducibility of analysis. To the best of our knowledge, there is not any \proglang{R}-package or framework adjusted for the special case of small area estimation which provides a simulation environment.

The aim of this article is to introduce a new \proglang{R}-package, \proglang{saeSim}, which supports the process of making simulation studies in the field of small area estimation reproducible. To be more precise, the package has three main objectives: First, provide tools for data generation. Second, unify the process of simulation studies. Third, make the source code of simulation studies available, such that it supports the conducted research in a transparent manner.

@@

The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where few or no sampled units are available. Groups may be areas or other entities, for example defined by socio-economic characteristics. The demand for such estimators is rising as they are used for fund allocation, educational and health programs \citep{pfeffermann13}. As direct estimation of such statistics are considered to be unreliable (with respect to MSE), methods in small area estimation try to improve the domain predictions by borrowing strength from neighbouring or \textit{similar} domains. This can be achieved by using additional information from census data or registers to assist the prediction for non-sampled domains or domains with small sample sizes.

@@

Due to reasons of confidentiality unit-level information is not always available. Instead only aggregates for the domains or direct estimators may be supplied. In this case the feasible direct estimates are known to be unreliable in the case of small sample sizes. Here area-level models can be valuable. The area-level model introduced by \cite{fay79} is built on a sampling model:
%
\[\directStat_{\indexDomain} = \trueStat_{\indexDomain} + \samplingError_{\indexDomain},\]
%
where $\directStat_{\indexDomain}$ is a direct estimator of a statistic of interest $\trueStat_{\indexDomain}$ for an area $\indexDomain$. The sampling error $\samplingError_{\indexDomain}$ is assumed to be independent and normally distributed with known variances $\samplingVarianceIndexed$, i.e. $\samplingError_{\indexDomain}|\trueStat_{\indexDomain} \sim \mathit{N}(0, \samplingVarianceIndexed)$. The model assumes a linear relationship between the true area statistic $\trueStat_{\indexDomain}$ and some auxiliary variables $\xArea$:
%
\[\trueStat_{\indexDomain} = \xArea^\top \beta + \randomEffectIndexed,\] 
%
with $\indexDomain=1,\dots, \nDomains$. 
%Note that $\xArea$ is a vector containing area-level (aggregated) information for $\nRegressor$ variables and $\beta$ is a vector ($1\times \nRegressor$) of regression coefficients describing the (linear) relationship. 
The model errors $\randomEffectIndexed$ are assumed to be independent and normally distributed, i.e. $\randomEffectIndexed \sim \mathit{N}(0, \randomEffectVariance)$. Furthermore $\samplingErrorIndexed$ and $\randomEffectIndexed$ are assumed to be independent. Combining the sampling and linking model leads to:
\begin{equation}
\label{eq:FH}
\directStatIndexed = \xArea^\top \beta + \randomEffectIndexed + \samplingErrorIndexed.
\end{equation} 
%
The Fay-Herriot (FH) model in (\ref{eq:FH}) is effectively a random-intercept model where the distribution of the error term $\samplingErrorIndexed$ is heterogeneous and known. The EBLUP of the small area mean in the FH model is given by 
\begin{eqnarray}\label{FHEBLUP}\hat{\overline{y}}_i^{FH}&=&\xArea^\top \hat{\beta} + \hat{\randomEffectIndexed}.
\end{eqnarray}

@@

Simulation studies in small area estimation address three different levels, the population, the sample and data on aggregated level. Figure \ref{fig:flowdiagram} illustrates these levels. The left column describes the steps of data manipulation, the right column presents the function names to define the corresponding steps. The \textbf{population-level} defines the data on which a study is conducted and may be a true population, synthetic population data or randomly generated variates from a model. We see two different points of view to define a population: Firstly, \textit{design-based} simulations, which means that a simulation study is based on true or synthetic data of \textit{one} population. Secondly, \textit{model-based} simulations, which have changing random populations drawn from a model.

@@

\section{Case studies}
\label{sec:caseStudy}
We present two applications of \proglang{saeSim}, one model-based simulation in Section \ref{sec:csModel} and a design-based simulation in Section \ref{sec:csDesign}. Before, we introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation. The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}. \red{As a simple example see the following lines which are equivalent with respect to their functionality:}

<<eval=FALSE>>=
library(magrittr)
colMeans(matrix(rnorm(10), ncol = 2))
rnorm(10) %>% matrix(ncol = 2) %>% colMeans
@

In \proglang{saeSim}, we rely on this operator. Although all functions can be used without it, we strongly recommend its usage. The following example shows some of the aspects of the package:

<<eval=TRUE, echo=FALSE>>=
library(saeSim)
@

<<eval=FALSE>>=
library(saeSim)
setup1 <- sim_base_lm() %>% sim_sample(sample_number(5))
setup2 <- sim_base_lm() %>% sim_sample(sample_fraction(0.05))
@
